Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-11 paper/paper.tex
minor tweaks to LaTex so it compiles

\newcommand{\jdbcomment}[1]{\emph{\color{red} [#1]}}

@@

To create the type III interferon reporters, a 1.2kb region upstream of the human IL29 (IFNL1) gene was cloned into the pHAGE2 vector, with the native Kozak sequence retained at the 3' end. 
Downstream of this promoter we cloned ZsGreen translationally linked to LNGFR$\Delta$C via a P2A linker.
The sequence of this construct is provided in \FIGDATA[IFNrare]{reporter_sequences}.

@@

For titering virus by qPCR, vRNA was harvested from 80 μl of viral supernatant by the addition of 600 μl of RLT plus before proceeding with the standard QIAGEN RNeasy Plus Mini kit protocol. The cDNA was generated using SuperScript III first-strand synthesis supermix using the manufacturer’s protocol, and using the universal vRNA primers of Hoffmann et al. (add Hoffman ref) with the modifications described in Xue et al. (add Katherine ref). The qPCR was then performed as for mRNA measurements

>>>>

\newcommand{\jdbcomment}[1]{\emph{\color{red} [#1]}}
\newcommand{\abrcomment}[1]{\emph{\color{blue} [#1]}}

@@

To create the type III interferon reporters, a 1.2kb region upstream of the human IL29 (IFNL1) gene was cloned into the pHAGE2 vector, with the native Kozak sequence retained at the 3' end. 
Downstream of this promoter we cloned LNGFR$\Delta$C linked to ZsGreen via a P2A linker.
The sequence of this construct is provided in \FIGDATA[IFNrare]{reporter_sequences}.

@@

For titering virus by qPCR, vRNA was harvested from 80 $\mu$l of viral supernatant by the addition of 600 $\mu$l of RLT plus before proceeding with the standard QIAGEN RNeasy Plus Mini kit protocol. The cDNA was generated using SuperScript III first-strand synthesis supermix using the manufacturer’s protocol, and using the universal vRNA primers of Hoffmann et al. (add Hoffman ref) with the modifications described in Xue et al. (add Katherine ref). The qPCR was then performed as for mRNA measurements
